---
title: "Supplementary Information"
author: "T. Florian Jaeger and Shawn Cummings"
date: "\today"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  fontsize: 10pt
geometry: margin=2cm
header-includes:
- \usepackage{booktabs}
- \usepackage{siunitx}
- \usepackage{tabto}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage{placeins}
- \usepackage{lscape}
- \usepackage{animate}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \makeatletter\renewcommand{\fps@table}{!ht}\makeatother
- \setstcolor{red}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \subsectionfont{\color{blue}}
- \subsubsectionfont{\color{darkgray}}
---

```{r, include=FALSE}
library(tidyverse)
library(magrittr)    # pipes
library(ggtext)      # markdown formatting for text elements
library(ggforce)     # facet matrix
library(plotly)      # 3D plots
library(lubridate)   # date conversion, etc.

library(brms)        # Bayesian GL(M)Ms
library(tidybayes)   # extract posterior from brmfits
library(modelr)      # create data grids
library(sjPlot)      # tables for Bayesian GL(M)Ms
library(broom)       # extracting information from GL(M)Ms
library(boot)        # easy logit() function

library(knitr)
library(linguisticsdown)  #IPA symbols
library(rstan)

# Setting up cmdstanr
# library(curl)
# if (has_internet()) install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
library(cmdstanr)
# install_cmdstan()
```

```{r constants, include=FALSE}
source("constants.R")
```

```{r, include=FALSE}
opts_chunk$set(dev = 'png', dpi = 96,
               comment="",
               echo=FALSE, warning=TRUE, message=FALSE,
               cache=FALSE,
               size="small",
               tidy.opts = list(width.cutoff = 200),
               fig.width = fig.base_width, fig.height = fig.base_height, fig.align = "center")

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

color_block = function(color) {
  function(x, options) sprintf('\\color{%s}\\begin{verbatim}%s\\end{verbatim}\\color{black}',
                               color, x)
}
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
```

# Context statement
This document contains the data preparation, visualization, and analyses reported in the main text. As of 2022, the Human Language Processing Lab at the University of Rochester is committed to producing articles and supplementary information in the form of R Markdown documents whenever possible. This particular project grew out of a yearlong undergraduate research class (BCS 206/7 "Undergraduate Research in Cognitive Science"). To accommodate differences in familiarity with R programming, and to facilitate project workflow, the authors agreed to write the main text in a common word processing software, and to provide this R Markdown document as supplementary information.

# Chronology of Experiments

 * **Experiment 1a:** test-only experiment (N = 64) conducted over MTurk between 01/20-22/2021.
 * **Experiment 1b:** test-only experiment (N = 64) conducted over MTurk between 03/03-04/2021.
 * **Experiment 1c:** test-only experiment (N = 64) conducted over MTurk between 06/03-05/2021.
 * **Experiment 2:** test-only experiment (N = 64) conducted over MTurk between  07/14-15/2021.
 * **Experiment 2b:** test-only experiment (N = 64) conducted over MTurk between 07/23-24/2021.

```{r}
d.CISP.ALL <-
  read.csv("../data/CISP_data.csv") %>%
  mutate(
    across(
      .cols = c(starts_with("Participant"), -Participant.Age, 
                Phase, starts_with("Condition"), -Condition.Test.Audio, 
                starts_with("Item"), starts_with("Talker"),
                Response, Task, Exclude_Participant.Reason), 
      .fns = factor),
    across(
      .cols = c(Participant.Age, Condition.Test.Audio, Response.RT, starts_with("Duration")),
      .fns = as.numeric),
    across(
      .cols = c(Item.isCatchTrial, Response.CatchTrial),
      .fns = as.logical))

get_demographics <- function(data, experiment = unique(data$Experiment)) {
  data %<>%
    filter(Experiment %in% experiment) %>%
    select(ParticipantID, starts_with("Participant")) %>%
    distinct() %>%
    mutate(across(-Participant.Age, as.character)) %>%
    replace_na(list(Participant.Sex = "unknown", Participant.Race = "unknown", Participant.Ethnicity = "unknown"))
  
  print(round(prop.table(table(data$Participant.Sex)) * 100, 1))
  print(round(prop.table(table(data$Participant.Ethnicity)) * 100, 1))
  print(round(prop.table(table(data$Participant.Race)) * 100, 1))
  cat(paste0("Mean age = ", round(mean(data$Participant.Age, na.rm = T), 1), " (SD = ", round(sd(data$Participant.Age, na.rm = T), 1), "). Interquartile range = ", summary(data$Participant.Age)[2], "-", summary(data$Participant.Age)[5], ". Declined to report: ", percent(summary(data$Participant.Age)[7] / nrow(data))))
}
```

# Participant demographics

```{r}
get_demographics(data = d.CISP.ALL, experiment = c("CISP-1a", "CISP-1b", "CISP-1c", "CISP-2a", "CISP-2b"))
```

# Experiments 1a-c

## Data import

```{r}
d.test.Exp1 <- 
  d.CISP.ALL %>%
  filter(Experiment %in% c("CISP-1a", "CISP-1b", "CISP-1c"))

d.LJ18.test <-
  read.csv("../data/Liu Jaeger 2018/Liu-Jaeger-2018-test-1-s2.0-S0010027718300118-mmc2.csv") %>%
  # Filter to norming experiment
  filter(Condition == 'Filler') %>%
  mutate(
    Experiment = factor('LJ18-NORM'),
    ParticipantID = as.factor(paste0("LJ18.", Subject)),
    Condition.Test.Pen = "audio-only",
    Condition.Test.OriginalLabel = NA,
    Response = factor(case_when(Response == "SH" ~ "ASHI", Response == "S" ~ "ASI")),
    Response.ASHI = case_when(
      Response == "ASHI" ~ 1, 
      Response == "ASI" ~ 0,
      T ~ NA_integer_),
    # Blocks were 6 trials per block in LJ18 but 12 in CISP, so we re-calculate
    # blocks for LJ18 to be blocks of 12 trials.
    Block = Trial %/% 12 + 1,
    Trial = Trial + 1,
    Experiment.Platform = "MTurk",
    Exclude_Participant.because_of_TechnicalDifficulty = FALSE,
    across(c(Condition.Test.Pen, Condition.Test.OriginalLabel), factor)) %>%
    rename(Condition.Test.Audio = Step, Item.Filename = Filename, Response.RT = RT) %>%
  select(-c(X, Label, Condition, Subject))

d.test <- bind_rows(d.test.Exp1, d.LJ18.test)
```

## Materials: Selection of acoustic continuum steps
As described in the main text, we aimed to maximize the power to detect effects---like that of the pen in the mouth---along the *asi-ashi* continuum. Specifically, we aimed to select one step that, across all other manipulations, would yield approximated 25% *ashi* responses, four steps that would yield close to 50% *ashi* responses, and one step that would yield 75% *ashi* responses.

The intention for Experiment 1a was to employ the exact same acoustic steps as in @liu-jaeger2018: 12, 14, 15, 16, 17, and 19, where higher numbers indicate acoustically more ashi-like steps. However, a labeling mistake resulted in the steps being internally named with higher numbers indicating proportion of asi, rather than ashi. The actual steps that were used in Experiment 1a were 13, 15, 16, 17, 18, 20 unintentionally shifting the test continuum 1 step towards the ashi end, compared to @liu-jaeger2018. As we report below, Experiment 1a yielded overall more asi than ashi responses. Experiment 1b thus attempted to expand the test stimuli towards the ashi end of the continuum. However, as we still had not discovered the labeling mistake, we ended up expanding the continuum even further towards the asi end instead, with steps 10, 13, 14, 15, 16, 20. At this point, we identified the labeling mistake. Experiment 1c employed steps 13, 17, 18, 19, 20, and 24. We emphasize that the location of the test steps is not critical for Experiments 1a-c.

## Procedure: Further details on exit survey
<!-- TO DO SHAWN: could you fill in more information about the questions we asked, including a full list of questions? -->

For Experiment 1b, we made minor changes to the survey. We removed one question about audio quality which asked participants to rate the quality of their audio equipment as "bad", "good", "professional", etc. Previous analyses in our lab have found that the subjective nature of this question makes it hard to interpret. And, in order to encourage the participants to answer survey questions truthfully, we emphasized that they would get compensated independent of their answers, and that truthful answers would greatly help us with the interpretation of results. <!-- TO DO: please check whether this is all correct. I believe we have detailed notes about these changes both in an RMD file I created back then, and in the Javascript / survey code itself. -->

For Experiment 1c, we revised our questions about internet connectivity. Specifically, we changed the two questions that asked about video or sound issues during the experiment. We clarified that these questions were asking solely about technical issues, rather than any oddities between the alignment of the video and audio (as separate questions already assessed that aspect). The revised questions were introduced by the following statement: "The videos and sounds in this experiment were manipulated by aligning the same video with different sound sources. As a consequence, you might have noticed some 'jumps' or slightly odd-looking moments in the video. Here we are interested in *potential technical issues with the internet connection* beyond any oddities you might have noticed about how the video and sound aligned." (emphasis in original) Then two questions assessed whether the videos or sounds failed to load or stopped and restarted playing during exposure. As these revised questions explicitly mentioned that the videos and sounds had been manipulated, they were moved towards the end of the survey, so that they followed any questions that inquired about the pronunciation of the talker in the video (recall that participants could not go back to previously answered questions). <!-- TO DO: please check whether this is all correct. I believe we have detailed notes about these changes both in an RMD file I created back then, and in the Javascript / survey code itself. -->

## Exclusions

```{r exclusions, fig.width=3*fig.base_width, fig.height=fig.base_height}
# Make exclusion plot for only 1a-c
d.test.Exp1 <-
  d.test %>%
  run_exclusions(c("CISP-1a", "CISP-1b", "CISP-1c"))

# To also make sure exclusions have been applied LJ18
d.test %<>%
  excludeData() %>%
  filter(!is.na(Response.ASHI))

# mean(d.test %>% filter(Experiment %in% c("CISP-1a", "CISP-1b", "CISP-1c")) %>% pull(Duration.Assignment))
# sd(d.test %>% filter(Experiment %in% c("CISP-1a", "CISP-1b", "CISP-1c")) %>% pull(Duration.Assignment))
```

## Analyses

```{r}
p <- plot_data(d.test, experiment = c("CISP-1a", "CISP-1b", "CISP-1c"), background_experiment = "LJ18-NORM")
plot(p)

ggsave(
  p,
  file = "../figures/Experiment 1a-c.png",
  width = fig.base_width * 3,
  height = fig.base_height * 3 + .25)
```


### Experiment 1a

```{r, results='markup'}
m.Exp1a <- fit_test_model(data = d.test.Exp1, experiment = "CISP-1a")
my_hypotheses(m.Exp1a, experiment = "Exp 1a") %>% map(print) -> TEMP
```

Were any effects other than those of primary interest potentially credible?

```{r}
# Sanity check to see whether there are other significant effects, not included in hypothesis tests
summary(m.Exp1a)$fixed %>% filter(map2(`l-95% CI`, `u-95% CI`, ~ !between(0, .x, .y)) %>% unlist())
# plot_model_predictions(m.Exp1a)
```


### Experiment 1b

```{r, results='markup'}
m.Exp1b <- fit_test_model(d.test.Exp1, "CISP-1b")
my_hypotheses(m.Exp1b, experiment = "Exp 1b") %>% map(print) -> TEMP
```

Were any effects other than those of primary interest potentially credible?

```{r}
# Sanity check to see whether there are other significant effects, not included in hypothesis tests
summary(m.Exp1b)$fixed %>% filter(map2(`l-95% CI`, `u-95% CI`, ~ !between(0, .x, .y)) %>% unlist())
# plot_model_predictions(m.Exp1b)
```

### Experiment 1c

```{r, results='markup'}
m.Exp1c <- fit_test_model(d.test.Exp1, "CISP-1c")
my_hypotheses(m.Exp1c, experiment = "Exp 1c")  %>% map(print) -> TEMP
```

Were any effects other than those of primary interest potentially credible?

```{r}
# Sanity check to see whether there are other significant effects, not included in hypothesis tests
summary(m.Exp1c)$fixed %>% filter(map2(`l-95% CI`, `u-95% CI`, ~ !between(0, .x, .y)) %>% unlist())
# plot_model_predictions(m.Exp1c)
```

### Liu and Jaeger (2018, Experiment 1a-b)
For comparison, we also analyzed the "baseline" experiment from Liu and Jaeger (2018, Experiment 1a-b) with the same analysis approach employed in the present study. Like all previous work in this line of research, this baseline experiment employed audio-only test stimuli. Unlike our Experiments 1a-c, Liu and Jaeger's control experiment contained an exposure phase (with only typical fricative pronunications). We further note that none of Experiments 1a-c employed the exact same continuum steps as Liu and Jaeger (2018). It is known that the selection of acoustic continuum steps that participants experience in an experiment can affect their categorization responses: even the exact same continuum step can be categorized differently depending on the other steps included in the experiment (Yamata & Tohkura, 1992). These factors limit the extent to which our Experiments 1a-c can be directly compared to Liu and Jaeger's audio-only experiment. We thus focus only on the magnitude of the acoustic effects in Liu and Jaeger, compared to the present experiments.

```{r, results='markup'}
d.test.LJ18 <-
  d.test %>%
  run_exclusions(experiment = "LJ18-NORM")

m.LJ18 <- 
  fit_test_model(
    d.test.LJ18, 
    experiment = "LJ18-NORM", 
    formula = bf(Response.ASHI ~
                   1 + mo(Block) * mo(Condition.Test.Audio) +
                   (1 + mo(Condition.Test.Audio) | ParticipantID)))

my_LJ18_hypothesis <- 
  function(m, experiment = "LJ18-NORM") {
    format <-  
      . %>%
      rename(BF = Evid.Ratio) %>%
      mutate(
        Experiment = experiment,
        across(
          c("Estimate", "Est.Error", starts_with("CI"), "Post.Prob"),
          ~ signif(.x, 3)),
        BF = ifelse(is.infinite(BF), paste(">", ndraws(m)), as.character(round(BF, 1)))) %>%
      relocate(Experiment, everything())
    
    hypothesis(
      m,
      c("bsp_moCondition.Test.Audio > 0",
        "bsp_moBlock:moCondition.Test.Audio = 0"),
      class = NULL, scope = "standard") %>%
      .[["hypothesis"]] %>%
      mutate(
        Experiment = "LJ18-NORM",
        Hypothesis = c(
          "Acoustic continuum more ASHI-like -> more ASHI-responses",
          "Continuum effect is stable over blocks")) %>%
      format() %>%
      kable(caption = "Effects of acoustic continuum.")
  }

my_LJ18_hypothesis(m.LJ18)
```

Were any effects other than those of primary interest potentially credible?

```{r}
# Sanity check to see whether there are other significant effects, not included in hypothesis tests
summary(m.LJ18)$fixed %>% filter(map2(`l-95% CI`, `u-95% CI`, ~ !between(0, .x, .y)) %>% unlist())

# plot_model_predictions(m.LJ18)

# d.test.LJ18 %>%
#   droplevels() %>%
#   data_grid(ParticipantID, Condition.Test.Audio, Block = 1) %>%
#   add_epred_draws(m.LJ18, re_formula = NULL) %>%
#   ggplot(aes(x = Condition.Test.Audio, y = Response.ASHI)) +
#   stat_lineribbon(aes(y = .epred), color = "black") +
#   stat_summary(
#     data =
#       d.test.LJ18 %>%
#       filter(Block == 1) %>%
#       group_by(ParticipantID, Condition.Test.Audio) %>%
#       summarise(Response.ASHI = mean(Response.ASHI)),
#     geom = "pointrange",
#     color = "black") +
#   scale_fill_grey()
```

# Experiments 2 and 2b
We conducted two experiments that were designed to test whether listeners need to see the effects of the pen on the articulators *during the production of the fricative*, or whether the presence of a pen during the production of a fricative is sufficient to cause the effects observed in Experiments 1a-c. To this end, Experiments 2 and 2b introduced a black box that occluded the talker's mouth during the articulation of the fricative (see main text for details). The two experiments were identical except that Experiment 2b introduced an additional task intended to assure that participants paid attention to the videos (rather than just the audio). This change in procedure from Experiment 2 to 2b was intended to address an alternative explanation for the results of Experiment 2. As reported below, Experiment 2 did not find the effects of pen location that were present in Experiments 1a-c. This raised the question as to whether participants in Experiment 2 failed to pay attention to the video (unlike in Experiments 1a-c). 

On the one hand, the catch task employed in Experiment 2 (same as in Experiments 1a-c: participants were asked to press "B" when they saw a white dot in the video) would seem to reject that possibility: as in Experiments 1a-c, participants that pressed "B" in the absence of a white dot were excluded from the analysis of Experiment 2. However, since none of the trials actually contained a white dot, this means that participants that did not pay any attention to the video and never pressed "B" would fail to be excluded from the analysis of Experiment 2. In Experiment 2b, we thus replaced the catch task from Experiments 1a-c & 2, and instead asked Experiments to press SPACE when the pen was in the mouth. As in Experiment 2, participants in Experiment 2b also had to press "X" or "M" to indicate whether they heard *asi* or *ashi*. 

## Data import
```{r}
d.test.Exp2 <- 
  d.CISP.ALL %>%
  filter(Experiment %in% c("CISP-2a","CISP-2b")) %>%
  # Make CISP-2a the default CISP-2 for visualizations below
  mutate(
    Experiment = 
      case_when(
        Experiment == "CISP-2a" ~ "CISP-2",
        T ~ Experiment),
    Response.CatchCorrect = 
      case_when(
        Experiment == "CISP-2" & Response.CatchTrial == Item.isCatchTrial ~ 1,
        Experiment == "CISP-2" & Response.CatchTrial != Item.isCatchTrial ~ 0,
        Experiment == "CISP-2b" & Response.CatchTrial == (Condition.Test.Pen == "M") ~ 1,
        Experiment == "CISP-2b" & Response.CatchTrial != (Condition.Test.Pen == "M") ~ 0,
        T ~ NA_integer_))
```

## Procedure
Experiment 2 employed the exact same tasks as Experiment 1a-c. Experiment 2b, however, introduced an additional task. Participants were asked to press SPACE whenever the pen was in the talker's mouth. After pressing SPACE, participants had to answer whether they heard *asi* or *ashi*, as in all preceding experiments. Figure \@ref(fig:XXX) shows a screenshot of the specific instructions.

<!-- TO DO: Shawn, can we add the screen shot from your email here, or perhaps a screen shot of the entire screen, incl. the part you had in your email -->

## Exclusions
Figure \@ref(fig:XXX) summarized the exclusions for Experiment 2 and 2b. Of note is the high exclusion rate for Experiment 2b, for which almost one fourth of all participants stated after the experiment that they had not been wearing head phones. This deterioration of data quality for experiments conducted over Mechanical Turk post 2020 was also observed in other experiments conducted in our lab during the same time period. Like in the present study, data quality tended to decrease in particular for the later studies of a series of experiments. One possible explanation is our recruitment criterion, which only allowed participants to see the experiment if they had *not* participated in any previous experiment of the series. This successively reduces the participant pool, potentially making experiments in a series increasingly more vulnerable to less cooperative participants. This motivated our switch to the Prolific crowdsourcing platform for subsequent experiments. Experiment 2b was the last experiment we conducted over Mechanical Turk. <!-- TO DO: correct? -->

```{r}
d.test.Exp2 %<>% run_exclusions(c("CISP-2", "CISP-2b"))
```

## Analyses - Experiment 2

```{r}
p <-
  plot_data(
    bind_rows(d.test.Exp1, d.test.Exp2),
    experiment = "CISP-2", background_experiment = "CISP-1c")
plot(p)

ggsave(
  p,
  file = "../figures/Experiment 2.png",
  width = fig.base_width * 3,
  height = fig.base_height + .5)
```

```{r, results='markup'}
m.Exp2 <- fit_test_model(d.test.Exp2, experiment = "CISP-2")
my_hypotheses(m.Exp2, experiment = "Exp 2") %>% map(print) -> TEMP
# plot_model_predictions(m.Exp2)
```

### Comparison of Experiment 2 against Experiment 1c
The following graphs show the predictions for the effect of pen location in both Experiments 2 and 1c, based on a model fit to the data from both experiments (while allowing Experiment to interact with all other predictors):

```{r}
m.Exp2vsExp1c <- fit_test_model(data = bind_rows(d.test.Exp1, d.test.Exp2), experiment = c("CISP-1c", "CISP-2"))

condition_effects_formatting <-
  list(  
    scale_color_discrete("Pen", breaks = c("H", "M"), labels = c("hand", "mouth")),
    scale_fill_discrete("Pen", breaks = c("H", "M"), labels = c("hand", "mouth")),
    scale_x_continuous("Acoustic evidence"),
    scale_y_continuous("log-odds of ASHI-response"))
ce <-
  conditional_effects(
    m.Exp2vsExp1c,
    effects = "Condition.Test.Audio:Condition.Test.Pen",
    # adding random effects NULL (or not: set to NA)
    re_formula = NA,
    conditions = make_conditions(
      x = bind_rows(d.test.Exp1, d.test.Exp2) %>%
        filter(Experiment %in% c("CISP-1c", "CISP-2")),
      vars = c("Experiment", "Condition.Test.OriginalLabel")) %>%
      mutate(
        Block = 0,
        cond__ = paste0(
          ifelse(Experiment == "CISP-1c", "Exp 1c (no occluder)", "Exp 2 (occluder)"),
          ":Visual label=", Condition.Test.OriginalLabel)),
    robust = T,
    method = "posterior_linpred")
p <- plot(ce, facet_args = list(ncol = 2), plot = F)
p[[1]] + condition_effects_formatting
```

If the effects of pen location in Experiments 1a-c were due to the pen visually occluding otherwise available visual cues to articulatorily relevant evidence, then both pen locations in Experiment 2 should yield *ashi*-responses similar to the pen-in-mouth condition of Experiment 1c (which used the exact same audio-visual stimuli as Experiment 2, except without a visual occluder). To test this hypothesis, we combined the data from Experiments 1c and 2, and coded both pen locations of Experiment 2 as a single new pen location ("occluded"). We then analyzed this combined data in the exact same way as Experiments 1c and 2, except that pen location now was a 3-way sliding difference-coded factor, testing (1) whether the occluded condition (Experiment 2) elicited fewer *ashi* responses than the pen-in-hand condition of Experiment 1c (as predicted by the occlusion hypothesis) and (2) whether the pen-in-mouth condition of Experiment 1c yielded fewer *ashi* responses than the occluded condition (as predicted if occlusion does *not* explain all of the effects of pen location in Experiments 1a-c).

```{r}
m.Exp2vsExp1c <- 
  fit_test_model(
    data = 
      bind_rows(d.test.Exp1, d.test.Exp2) %>%
      prep_for_analysis() %>%
      mutate(
        Condition.Test.Pen = 
          factor(
            ifelse(Experiment == "CISP-2", "O", as.character(Condition.Test.Pen)),
            levels = c("H", "O", "M")),
        Condition.Test.Pen = 
          "contrasts<-"(factor(Condition.Test.Pen), , 
                        cbind("OvsH" = c(-2/3, 1/3, 1/3), "MvsO" = c(-1/3, -1/3, 2/3)))),
    experiment = c("CISP-1c", "CISP-2"),
    formula = bf(Response.ASHI ~ 1 + Condition.Test.OriginalLabel * Condition.Test.Pen * mo(Block) * mo(Condition.Test.Audio) + 
                   (1 + Condition.Test.OriginalLabel * Condition.Test.Pen * mo(Condition.Test.Audio) | ParticipantID)),
    file = "../models/Exp-CISP-2-vs-CISP-1c-occlusion-test")
```

Overall, the results of this analysis do not provide any notable evidence for the occlusion hypothesis while providing strong evidence for the compensation hypothesis. In the middle of the acoustic continuum, *ashi*-responses were *more* likely in Experiment 2, compared to even the pen-in-hand condition of Experiment 1c (BF = 2). This is the opposite of what would be expected if the main effects of pen location in Experiments 1a-c were due to visual occlusion. There also was strong evidence that the pen-in-mouth condition of Experiment 1c resulted in fewer *ashi*-responses than in Experiment 2 (BF = 73.1). 

The only way in which the visual occluder in Experiment 2 resembled the pen-in-mouth condition in Experiment 1c was in terms of their interaction with visual evidence to the articulation of "sh": both the black rectangle in Experiment 2 and the pen-in-the-mouth in Experiment 1c reduced the effect of visually *ashi*-like stimuli, compared to the pen-in-hand condition (see third row of the two tables). These two effects were almost identical (comparison of occluder vs. pen-in-hand condition: BF = 14.2; comparison of pen-in-mouth vs. occluder condition: BF = .9). This result is not particularly surprising given that the black rectangle completely occluded any direct visual evidence of "s" vs. "sh" articulation. 

```{r, results='markup'}
hypothesis(m.Exp2vsExp1c, 
           c("b_Condition.Test.PenOvsH + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.PenOvsH < 0", 
             "bsp_moCondition.Test.Audio:Condition.Test.PenOvsH < 0", 
             "b_Condition.Test.OriginalLabelSH:Condition.Test.PenOvsH + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenOvsH < 0",
             "bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenOvsH< 0"), class = NULL, robust = T) %>%
      .[["hypothesis"]] %>% 
      mutate(Hypothesis = c(
        "Pen location Mouth -> fewer ASHI-responses",
        "Pen effect increases for more ASHI-like acoustic input",
        "Pen effect increases for visually ASHI-biased input",
        "Pen effect increases even more when acoustic and visual input is ASHI-biased")) %>%
      format_hypothesis_tables("Exp 2 vs. 1c") %>%
      kable(caption = "Effects of pen location: occlusion vs. hand")

hypothesis(m.Exp2vsExp1c, 
           c("b_Condition.Test.PenMvsO + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.PenMvsO < 0",
             "bsp_moCondition.Test.Audio:Condition.Test.PenMvsO < 0", 
             "b_Condition.Test.OriginalLabelSH:Condition.Test.PenMvsO + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenMvsO < 0", 
             "bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenMvsO < 0"), class = NULL, robust = T) %>%
      .[["hypothesis"]] %>% 
      mutate(Hypothesis = c(
        "Pen location Mouth -> fewer ASHI-responses",
        "Pen effect increases for more ASHI-like acoustic input",
        "Pen effect increases for visually ASHI-biased input",
        "Pen effect increases even more when acoustic and visual input is ASHI-biased")) %>%
      format_hypothesis_tables("Exp 2 vs. 1c") %>%
      kable(caption = "Effects of pen location: mouth vs. occlusion")

# hypothesis(m.Exp2vsExp1c, 
#            c("b_Condition.Test.OriginalLabelSH:Condition.Test.PenOvsH + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenOvsH + b_Condition.Test.OriginalLabelSH:Condition.Test.PenMvsO + 2.5 * bsp_moCondition.Test.Audio:Condition.Test.OriginalLabelSH:Condition.Test.PenMvsO < 0"), class = NULL, robust = T) 
```



## Analysis - Experiment 2b
We first analyzed participants' accuracy in detecting when the pen was in talker's mouth, in which case participants were supposed to press SPACE. Then we turn to the analysis of participants' categorization responses.

### SPACE bar presses
When the pen was in the talker's mouth, participants were only slightly above chance (`r percent(d.test.Exp2 %>% filter(Experiment == "CISP-2b", Condition.Test.Pen == "M") %>% summarise(y = mean(Response.CatchCorrect)) %>% pull(y))` accurate). When the pen was in the talker's hand, participants were much more accurate (`r percent(d.test.Exp2 %>% filter(Experiment == "CISP-2b", Condition.Test.Pen == "H") %>% summarise(y = mean(Response.CatchCorrect)) %>% pull(y))`). This asymmetry is not particularly surprising: correct detection of the pen in the mouth required a key press, whereas correct detection that the pen was not in the mouth (but rather in the hand) required no action at all. Critically, participants' overall accuracy was above chance (`r percent(d.test.Exp2 %>% filter(Experiment == "CISP-2b") %>% summarise(y = mean(Response.CatchCorrect)) %>% pull(y))`). Overall, this suggests that participants could detect the pen presence above chance, while also suggesting that participants experienced the task to be difficult.

```{r}
# In Exp 2b, we used the catch trial functionality to ask participants whether the pen was in the mouth
# (SPACE press) or not (nothing). The response was coded in Reponse.CatchTrial, which is TRUE when participants
# pressed SPACE and FALSE otherwise.
d.test.Exp2 %>%
  filter(Experiment == "CISP-2b") %>%
  group_by(ParticipantID, Condition.Test.Pen, Exclude_Participant.because_of_IgnoredInstructions) %>%
  summarise(Response.CatchCorrect = mean(Response.CatchCorrect)) %>%
  ggplot(aes(x = Condition.Test.Pen, y = Response.CatchCorrect, shape = Condition.Test.Pen)) + 
  geom_point(alpha = .25) +
  geom_line(aes(group = ParticipantID), alpha = .25) +
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", size = 1) +
  scale_x_discrete(
    "Pen location",
    breaks = levels.test.pen_locations,
    labels = labels.test.pen_locations) +
  scale_y_continuous("Proportion correct responses about pen location", limits = c(0, 1)) +
  scale_shape_manual(
    "Pen location",
    breaks = levels.test.pen_locations, labels = labels.test.pen_locations, values = shapes.test.pen_locations)
```

```{r}
d.test.Exp2 %<>%
  select(-Exclude_Participant.because_of_IgnoredInstructions) %>%
  left_join(
    d.test.Exp2 %>% 
      filter(Experiment == "CISP-2b") %>% 
      group_by(ParticipantID, Condition.Test.Pen, Exclude_Participant.because_of_IgnoredInstructions) %>% 
      summarise(Response.CatchCorrect = mean(Response.CatchCorrect)) %>% 
      group_by(ParticipantID, Exclude_Participant.because_of_IgnoredInstructions) %>% 
      summarise(difference = abs(Response.CatchCorrect[1] - Response.CatchCorrect[2])) %>% 
      mutate(Exclude_Participant.because_of_IgnoredInstructions = 
               ifelse(difference > .9, TRUE, Exclude_Participant.because_of_IgnoredInstructions)) %>%
      select(-difference))
```

A closer look at participants' SPACE responses reveals that some participants almost never pressed the SPACE bar and some always pressed the SPACE bar, regardless of whether the pen was in the mouth (the lines forming the "X" in the figure). For example, `r nrow(d.test.Exp2 %>% distinct(ParticipantID, Exclude_Participant.because_of_IgnoredInstructions) %>% filter(Exclude_Participant.because_of_IgnoredInstructions))` (`r percent(nrow(d.test.Exp2 %>% distinct(ParticipantID, Exclude_Participant.because_of_IgnoredInstructions) %>% filter(Exclude_Participant.because_of_IgnoredInstructions)) / nrow(d.test.Exp2 %>% distinct(ParticipantID, Exclude_Participant.because_of_IgnoredInstructions)))`) participants pressed SPACE on 90% or more of all trials or did not press SPACE on 90% or more of the trials (all but one of these participants, never pressed SPACE). If those participants are excluded from the analysis, performance improved to `r percent(d.test.Exp2 %>% filter(Experiment == "CISP-2b" & !Exclude_Participant.because_of_IgnoredInstructions) %>% summarise(y = mean(Response.CatchCorrect)) %>% pull(y))` accuracy, with statistically indistinguishable performance when the pen was in the mouth vs. hand. 

We note that, in total, about half of the participants in Experiment 2b did not follow instructions---either by not wearing headphones for the experiment or by never/always pressing SPACE. As mentioned under Exclusions, we have encountered similar issues with data quality over Mechanical Turk over recent years whenever we conducted series of experiments (for which any subsequent experiment only recruits from the pool of participants that have *not* taken any previous experiments in the series). While we see no reason why the data from cooperative participants in Experiment 2b should not be analyzed, the fact that only about 50% of all participants seem to meet this criterion limits the conclusions that can be drawn from this experiment.

### Categorization responses
Next, we turn to participants categorization responses---i.e., whether participants heard *asi* or *ashi*. Figure \@ref(fig:results-exp2b) summarizes participants' categorization responses. For this figure, we did not exclude the `r nrow(d.test.Exp2 %>% distinct(ParticipantID, Exclude_Participant.because_of_IgnoredInstructions) %>% filter(Exclude_Participant.because_of_IgnoredInstructions))` participants that never or always pressed SPACE. Separate analyses---not summarized here---did, however, show that the results are unchanged when those participants are excluded. Compared to Experiment 2, participants in Experiment 2b exhibited noticeably weaker effects of the acoustic continuum (more shallow slope in Figure \@ref(fig:results-exp2b)a). This suggests a trade-off introduced by the secondary task in Experiment 2b: either because participants focused more on the visual input, or because the categorization response was delivered *after* the response to the visual stimulus (SPACE press), participants' responses were less affected by the acoustic continuum. Critically, however, Experiment 2b replicates all effects found in Experiment 2.

(ref:results-exp2b) Summary of participants’ responses in Experiments 2b, depending on pen location and acoustic continuum step (Panel A) or visual bias (Panel B). For comparison, the results from Experiment 2 are shown in the background. The two experiments were identical except for the secondary task introduced in Experiment 2b.

```{r results-exp2b, fig.width=fig.base_width * 3, fig.height=fig.base_height + .5, fig.cap="(ref:results-exp2b)"}
p <-
  plot_data(
    bind_rows(d.test.Exp1, d.test.Exp2),
    experiment = "CISP-2b", background_experiment = "CISP-2")
plot(p)

ggsave(
  p,
  file = "../figures/Experiment 2b.png",
  width = fig.base_width * 3,
  height = fig.base_height + .5)
```

```{r, results='markup'}
m.Exp2b <- fit_test_model(d.test.Exp2, "CISP-2b")
my_hypotheses(m.Exp2b, experiment = "Exp 2b") %>% map(print) -> TEMP
# plot_model_predictions(m.Exp2b)
```



